### 2021-05-31 README.Rmd
more stuff

tic()
create_dyadyears() %>%
  # Add Gleditsch-Ward codes
  add_gwcode_to_cow() %>%
  # Add GML MIDs 
  add_mids() %>%
  # Add trade data
  add_cow_trade() %>%
  # Add capital-to-capital distance
  add_capital_distance() %>%
  # Add contiguity information
  add_contiguity() %>%
  # Add major power data
  add_cow_majors() %>%
  # Add democracy variables
  add_democracy() %>%
  # Add IGOs data
  add_igos() %>%
  # Add National Material Capabilities
  add_nmc() %>%
  # add alliance data from Correlates of War
  add_cow_alliance() %>%
  # add alliance data from ATOP
  add_atop_alliance() %>%
  # add minimum distance. No default, must specify "cow" or "gw"
  add_minimum_distance(system = "cow") %>%
  # add Archigos data
  add_archigos() %>%
  # add gross and surplus GDP data
  add_sdp_gdp(system = "cow") %>%
  # you should probably filter to politically relevant dyads earlier than later...
  # Or not, it's your time and computer processor...
  filter_prd()
toc()

>>>>

tic()
create_dyadyears() %>%
  # Add GML MIDs 
  add_gml_mids(keep=NULL) %>%
  # Add Correlates of War MIDs 
  add_cow_mids(keep=NULL) %>%
  # add peace years
  add_peace_years() %>%
  # Add Gleditsch-Ward codes, because we can
  add_gwcode_to_cow() %>%
  # Add strategic rivalry data
  add_strategic_rivalries() %>%
  # Add trade data
  add_cow_trade() %>%
  # Add capital-to-capital distance
  add_capital_distance() %>%
  # Add contiguity information
  add_contiguity() %>%
  # Add major power data
  add_cow_majors() %>%
  # Add democracy variables
  add_democracy() %>%
  # Add IGOs data
  add_igos() %>%
  # Add National Material Capabilities
  add_nmc() %>%
  # add alliance data from Correlates of War
  add_cow_alliance() %>%
  # add alliance data from ATOP
  add_atop_alliance() %>%
  # add minimum distance. No default, must specify "cow" or "gw"
  add_minimum_distance(system = "cow") %>%
  # add Archigos data
  add_archigos() %>%
  # add gross and surplus GDP data
  add_sdp_gdp(system = "cow") %>%
  # you should probably filter to politically relevant dyads earlier than later...
  # Or not, it's your time and computer processor...
  filter_prd()
toc()
